Identification and performance of stock-recruitment functions in state

### 2024-02-12 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
inserted missing slide

##  $\Delta$AIC  - Median and 95% probability interval
- Smaller $\Delta$AIC when $\sigma_{R}$ is larger

>>>>

##  $\Delta$AIC  - Median and 95% probability interval
- Smaller $\Delta$AIC for BH with high fishing contrast, low $\sigma_{R}$ (but not necessarily correct BH); $\Delta$AIC is larger for mean SRR in these cases
- When $\sigma_{R}$ is larger and/or there is low contrast in fishing, the mean SRR is favored
